
\chapter{Contract NftRoot}

\minitoc

\section{Overview}


\issueMajor{No way to get funds back}{
    Tokens sent to the contract are locked forever.
    %
    They are sent when IndexBasis are destroyed and when
    contracts are deployed. The contract should provide a function
    to recover accumulated funds, or specify that these funds are used
    for long-term storage.
}

\section{Contract Inheritance}


\noindent\begin{tabular}{|l|p{5cm}|}\hline
DataResolver & \\\hline
IndexResolver & \\\hline
\end{tabular}


\section{Variable Definitions}


\ifsoltables
\noindent\begin{tabular}{|l|l|p{5cm}|}\hline
uint256 & \_{}totalMinted &  \\\hline
 & & assigned in @1.NftRoot.mintNft\\\hline
 & & used in @1.NftRoot.mintNft\\\hline
 & & used in @1.NftRoot.mintNft\\\hline
address & \_{}addrBasis &  \\\hline
 & & used in @1.NftRoot.destructBasis\\\hline
 & & assigned in @1.NftRoot.deployBasis\\\hline
 & & used in @1.NftRoot.deployBasis\\\hline
\end{tabular}
\fi

\begin{lstlisting}[firstnumber=16]
    uint256 _totalMinted;
\end{lstlisting}

\begin{lstlisting}[firstnumber=17]
    address _addrBasis;
\end{lstlisting}


\section{Constructor Definitions}


\subsection{Constructor}

\issueMinor{Variable initialization}{
    The globals \_totalMinted and \_addrBasis are not initialized.
}

\issueMinor{Code initialization}{ Anyone can build a NftRoot contract
  with a fake {\tt \_codeData} and {\tt \_codeIndex} ; consider checking the
  contract hashes.  }

\issueMinor{Code initialization}{ It is usually a bad practice to
  initialize variables containing code cells in constructors, as
  deployment messages are limited to 16kB.  }

\begin{lstlisting}[firstnumber=19]
    constructor(TvmCell codeIndex, TvmCell codeData) public {
        tvm.accept();
        _codeIndex = codeIndex;
        _codeData = codeData;
    }
\end{lstlisting}

\section{Public Method Definitions}


\subsection{Function deployBasis}

\issueCritical{Multiple calls may lead to leakage of {\tt IndexBasis}
  contracts}{ {\tt \_addrBasis} is updated after every call to {\tt
    deployBasis}, hence a call to this function forbids the deletion
  of the previously deployed {\tt IndexBasis}. If only one {\tt
    IndexBasis} contract should be created, the function should {\tt
    require} that {\tt \_addrBasis} is null before deploying a new
  contract. Otherwise, {\tt destructBasis} should receive {\tt
    codeIndexBasis} as argument too, to be able to recompute the
  corresponding contract address to destruct.}

\issueMinor{Constants}{ Values "0.5 ton", "0.4 ton" and "104" should
  be defined as constants (would improve readability) }

\issueMinor{Variable name typo}{
     Variable {\tt codeHasData} should be named {\tt codeHashData}. 
}

\begin{lstlisting}[firstnumber=33]
    function deployBasis(TvmCell codeIndexBasis) public {
        require(msg.value > 0.5 ton, 104);
        uint256 codeHasData = resolveCodeHashData();
        TvmCell state = tvm.buildStateInit({
            contr: IndexBasis,
            varInit: {
                _codeHashData: codeHasData,
                _addrRoot: address(this)
            },
            code: codeIndexBasis
        });
        _addrBasis = new IndexBasis{stateInit: state, value: 0.4 ton}();
    }
\end{lstlisting}

\subsection{Function destructBasis}

\issueCritical{Function should not be public}{ This function can be
  called by anyone (no check on sender), so that anybody can destroy
  {\tt IndexBasis} contracts; the authentification of destruct in
  IndexBasis is useless. }

\issueMinor{Check {\tt \_addrBasis} is not zero}{ Before destroying
  the contract pointed to by {\tt \_addrBasis}, the contract should
  check that the variable is not zero, or fail.}

\issueMinor{Set {\tt \_addrBasis} to zero}{After destroying a
  contract, the function should set the {\tt \_addrBasis} variable to
  zero.}

\begin{lstlisting}[firstnumber=47]
    function destructBasis() public view {
        IIndexBasis(_addrBasis).destruct();
    }
\end{lstlisting}

\subsection{Function mintNft}

\issueMinor{Constants}{
    Value "1.1 ton" should be defined as a constant.
}

\issueMinor{No check of {\tt msg.value}}{ The contract should check
  that enough balance is carried within {\tt msg.value} to deploy the
  contract. Otherwise, the {\tt \_totalMinted} value may be increased,
  but the contract will still fail to deploy the corresponding
  contract. }

%\issueMinor{Spurious variable name}{
%    \_totalMinted does not represent the total of NFT minted,
%    as the contract creation may bounce.
%}

%\issueMajor{Sender may be null}{
%    If a user calls "mintNft", a Data contract is deployed with
%    a null owner.
%}

\begin{lstlisting}[firstnumber=25]
    function mintNft() public {
        TvmCell codeData = _buildDataCode(address(this));
        TvmCell stateData = _buildDataState(codeData, _totalMinted);
        new Data{stateInit: stateData, value: 1.1 ton}(msg.sender, _codeIndex);

        _totalMinted++;
    }
\end{lstlisting}
